### 2016-09-19 Thesis/DCG_sb-wi-thesis-template/Proteasome/proteasome.tex
proteasome additions

\subsection{Statistical Analyses of LFQ-MS/MS Data Show Affinity Preparations Targeting Either the CP or RP Specifically Enrich for Their Respective Subcomplexes}
The LFQ-MS/MS data allowed us to perform a more formal statistical test for the enrichment of the RP over the CP in samples affinity purified from the RP subunits FLAG-RPT4a/b, and for the enrichment of the CP over the RP in samples affinity purified from CP subunit PAG1-FLAG. We estimated the distribution of RP and CP subunits in these samples using kernel density estimations (KDE) of MaxLFQ values as compared to our wild-type mock-affinity purifications as a negative control (Figure \ref{fig:volcanos} below each volcano plot, and larger plots in Figure S3).  As the KDE distributions were not normal, two non-parametric statistical tests, Kolmogorov-Smirnov (KS) and median test, were used to determine if there was specific enrichment of particular proteasome sub-complexes (RP vs CP) from the different affinity purifications. The KS test determines if the two distributions are different in shape or position, and the median test determines if the distribution’s medians are statistically different.

\begin{sidewaysfigure}[p]
	\centering
	\includegraphics[width=\columnwidth]{Proteasome/Volcanosplit1.png}
	\mycaption{Volcano Plots comparing proteasome affinity purifications under both plus and minus ATP conditions relative to WT controls, allow identification of statistically significant interacting partners for the proteasome}
	{Volcano plots comparing affinity purifications for PAG1-FLAG \textbf{(A and B)}, FLAG-RPT4a \textbf{(C and D)}, and FLAG-RPT4b \textbf{(E and F)} against their respective WT mock affinity purification control are shown. The top panels \textbf{(A, C, and E)} show comparisons for samples purified in the absence of ATP, while the lower panels \textbf{(B, D, and F)} show comparisons for samples purified in the presence of ATP. Two-dimensional Kernel Density Estimations (KDE) are shown for CP subunits in red and RP subunits in blue. Larger KDE plots are available in Figure S3. CP subunits are labeled as red squares, while RP subunits are labeled as blue squares. Proteins outside the dashed lines are statistically significantly differentially represented in purified samples relative to control as judged by a significant analysis of microarray or (SAM) test at 0.01 false discovery rate. Proteins likely involved in CP assembly are shown as green squares, while proteins likely involved in RP assembly are shown as yellow squares. Known proteasome associated proteins or PAPs are labeled as black squares, while unknown PAPs are labeled in grey squares. Proteins identified that did not reach SAM significance are labeled as grey circles.}
	\label{fig:volcanos1}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
	\ContinuedFloat
	\centering
	\includegraphics[width=\columnwidth]{Proteasome/Volcanosplit2.png}
	\mycaption{Volcano Plots comparing proteasome affinity purifications under both plus and minus ATP conditions relative to WT controls, allow identification of statistically significant interacting partners for the proteasome}
	{Volcano plots comparing affinity purifications for PAG1-FLAG \textbf{(A and B)}, FLAG-RPT4a \textbf{(C and D)}, and FLAG-RPT4b \textbf{(E and F)} against their respective WT mock affinity purification control are shown. The top panels \textbf{(A, C, and E)} show comparisons for samples purified in the absence of ATP, while the lower panels \textbf{(B, D, and F)} show comparisons for samples purified in the presence of ATP. Two-dimensional Kernel Density Estimations (KDE) are shown for CP subunits in red and RP subunits in blue. Larger KDE plots are available in Figure S3. CP subunits are labeled as red squares, while RP subunits are labeled as blue squares. Proteins outside the dashed lines are statistically significantly differentially represented in purified samples relative to control as judged by a significant analysis of microarray or (SAM) test at 0.01 false discovery rate. Proteins likely involved in CP assembly are shown as green squares, while proteins likely involved in RP assembly are shown as yellow squares. Known proteasome associated proteins or PAPs are labeled as black squares, while unknown PAPs are labeled in grey squares. Proteins identified that did not reach SAM significance are labeled as grey circles.}
	\label{fig:volcanos2}
\end{sidewaysfigure}

The KDE distribution for the CP as compared to the RP from samples affinity purified in the absence of ATP using PAG1-FLAG showed both the KS and the median \textit{p}-values being much less than 0.01, at 1.74E-10 and 4.3E-10, respectively (Figure 4 and S3 A). This suggests that the distributions are different, and that their medians were different with a greater than 20 fold increase in CP over RP. Conversely the KDE distributions for the samples affinity purified in the presence of ATP using PAG1-FLAG (Figure 4 and S3 B) overlap to a higher degree, with both the KS and Median \textit{p}-values > 0.01 at 0.401 and 0.256, respectively. This indicates that in samples affinity purified in the presence of ATP that the RP and CP distributions were not significantly different, and that their means were similar. Although not statistically significant, a 1.5 median fold change was observed for the CP over the RP in samples affinity purified in the presence of ATP using PAG1-FLAG suggesting that there may be some CP enriched as compared to the RP. These statistical analyses showed that, as expected, we were able to successfully enrich for the CP over the RP when affinity purifying from PAG1-FLAG expressing tissue.

	Conversely, in samples using the RP-based FLAG-RPT4a/b purified in the absence of ATP, the KDE distributions showed enrichment for the RP over the CP, with a fold change of 3.43 and 3.41 for the RPT4a and RPT4b subunits respectively (Figures 4 and Figures S3 C and E, respectively). Both the KS (3.303E-5 for RPT4a and 5.55E-5 for RPT4b) and median \textit{p}-values (7.11E5 for RPT4a and 7.11E-5 for RPT4b) were < 0.01, suggesting that the two distributions were statistically different and had different medians. Again, contrasting this with the samples purified in the presence of ATP using FLAG-RPT4a and FLAG-RPT4b (Figures 4 and Figures S3 D and F, respectively), the KDE distributions overlap with both the KS (0.017 for RPT4a and 0.058 for RPT4b) and median \textit{p}-values (0.089 for RPT4a and 0.023 for RPT4b) were > 0.01, suggesting that the RP and CP distributions are similar. Although not statistically significant, we still observed a two-fold-change enrichment in both FLAG-RPT4a/b samples purified in the presence of ATP for the RP over the CP. In summary, these KDE distributions and statistical analyses provide further support for enrichment of either the CP or the RP, as expected, when samples were affinity purified in the absence of ATP via PAG1-FLAG, or FLAG-RPT4a/b, respectively.

\subsection{Statistical Analysis of Affinity Purifications Enriched for the RP or CP Identifies Proteasome-Associated Proteins and Putative Assembly Chaperones Specific to Each Subcomplex}
	The ability to affinity-enrich both the CP and the RP from \textit{Arabidopsis} under gentle non-denaturing conditions without the need for high salt washes may enable identification of associated proteins, particularly those which may be more loosely bound. Additionally, targeting the RP or CP enables the identification of proteins that may be associating with either or both subcomplexes specifically. The previous data represented in Figure 3 showed the raw MaxLFQ values for some of the relevant associated proteins; however, a formal statistical test against mock affinity purifications was important given the high number of proteins identified and quantified via LFQ-MS/MS. To better understand the suite of proteins that are statistically enriched in samples that target the CP or RP specifically we compared the LFQ-MS/MS data obtained from our affinity purifications against their respective wild-type controls using volcano plots and SAM tests at 0.01 FDR.

Affinity purifications enriching for the CP via PAG1-FLAG, performed either in the presence or absence of ATP (Figure 4A and 4B respectively) show statistical enrichment for two orthologs of the UMP1 CP assembly chaperone, UMP1a and UMP1b. The \textit{Arabidopsis} genome encodes a third \textit{UMP1} ortholog, \textit{UMP1c}; however, we have no experimental evidence that UMP1c associates with the proteasome, even though it has several tryptic peptides from an extended C-terminal domain that could differentiate it from UMP1a/b (Figure S4). UMP1a, and UMP1b are considerably higher expressed at 90 and 55 ESTs as compared to UMP1c which had only 7 ESTs \citep{berardini15}, suggesting that UMP1c may be lowly expressed, or possibly a pseudogene.

Intriguingly, these samples also show statistical enrichment for a suite of putative CP assembly chaperones (Proteasome Biogenesis Associated Chaperone) PBAC1-4 (Figure 4A and 4B). Although their annotation in The \textit{Arabidopsis} Information Resource v10 (TAIR10) was incomplete, an InterProScan of their respective sequences supported these identifications (Table S3A). While PBAC1 was annotated as having a PBAC2 domain, the expectation value of 3.4E-6 was much lower than the expectation value of 1E-29 for the PBAC2 domains in the potential PBAC2 homologue. Additionally, PBAC1 and PBAC2 were previously identified by iterative PSI-BLAST with the human PAC1 and PAC2 orthologs in two separate studies \citep{kusmierczyk11, le07} which aids in our assignment of PBAC1 and PBAC2. This PSI-BLAST based analysis was repeated using human PAC1-4, which identified PBAC1-4 as the top hits for these proteins in \textit{Arabidopsis} (Table S3B). Protein sequence alignments for PBAC1-4 show that these proteins are conserved across plants but that they show little conservation with orthologs outside the plant kingdom with < 15\% protein sequence identity (Figure S5-S8).  All statistically significant interactors from PAG1-FLAG affinity purifications performed in both the presence or absence of ATP are available in Table S4.

As shown in Figure 4 C-F, UMP1a/b and PBAC1-4 were not significantly enriched in our affinity purifications targeting the RP, suggesting that these proteins interact with the CP specifically. However, affinity purifications that targeted the RP through either FLAG-RPT4a or FLAG-RPT4b showed statistically significant enrichment over controls for the putative orthologs of RP assembly chaperones HSM3, NAS2, and NAS6 (Figure 4 C-F). Importantly, these putative RP assembly chaperones were also absent from our affinity purifications that targeted the CP, suggesting that these proteins are RP specific interactors. All statistically significant interactors from FLAG-RPT4a and FLAG-RPT4b affinity purified in the presence or absence of ATP are available in Table S5 and Table S6. Several accessory proteins are common to both CP and RP purifications including the alternate capping particle PA200 \citep{book10}, ECM29 that is involved in stabilizing the CP-RP association \citep{lehmann10}, and the recently identified proteasome inhibitor 31 related protein PTRE1, which is involved in modulating proteasome activity in response to auxin \citep{yang16}.

\subsection{A Novel Plant Proteasome-Associated Protein, PAP1, Interacts with a Putative CP Assembly Chaperone}
An intriguing plant-specific protein, named here Proteasome Associated Protein 1 or PAP1 was identified and significantly enriched in affinity preparations that targeted the CP (Figure 4). While PAP1 had no domains of known function, as determined by InterProScan (Table S3A), it did contain a C-terminal HbYX (hydrophobic amino acid, followed by a tyrosine, followed by any amino acid) motif. This HbYX motif is commonly found in proteins that intercalate between the $\alpha$-rings of the CP \citep{kusmierczyk11}. This motif is found in both the plant specific PAP1, and in the assembly chaperone PBAC1 (Figure 5A) as well as the conserved yeast assembly chaperones Pba1 and Pba2 \citep{kusmierczyk11}. However, Pba2/PBAC2 orthologs outside of yeast typically contain a C-terminal HbF motif, with the only notable exception being the moss \textit{Physcomitrella patens} which instead contains a HbYX motif.   To confirm whether PAP1 did indeed interact with the proteasome, we generated transgenic plants expressing HA-tagged PAP1 in the \textit{PAG1::PAG1-FLAG pag1-1} background. Figure 5B shows immunoblots of SDS-PAGE separated samples from an affinity purification of HA-PAP1 utilizing anti-HA beads. HA-PAP1 expressed at very low levels in transgenic plants (Figure 5B, input). However, upon immunopurification and detection with anti-HA antibodies we were able to detect HA-PAP1, the FLAG-tagged CP $\alpha$-subunit PAG1, and the FLAG-less PAG1 product that likely resulted from cleavage of the FLAG tag during overnight incubation \citep{book10}. Low levels of both the CP $\beta$-subunit PBA1, and RPN1 subunit were also detected in these samples.

To identify which putative \textit{Arabidopsis} assembly chaperones might interact, we performed a yeast two-hybrid (Y2H) interaction assay for all pairwise combinations of PBAC1-4, and PAP1 (Figure 5C). We hypothesized that PAP1 may be a CP assembly chaperone and that it may interact with one or more of the other putative assembly chaperones. The Y2H showed pairwise interaction for PBAC1 and PBAC2, and pairwise interaction for PBAC3 and PBAC4 regardless of whether they were attached to the GAL4 activating or binding domains (Figure 5C). These interactions were consistent with how the CP assembly orthologs in other organisms interact \citep{murata09}.  Taken together these data suggested these proteins might form heterodimeric pairs, like other CP assembly chaperone orthologs. Importantly, we saw no interaction from PBAC1 or PBAC2 to PBAC3 or PBAC4 pairs in this Y2H, suggesting these putative assembly chaperones form separate complexes like their orthologs in mammals and yeast. Interestingly, we observed PAP1 interacting with PBAC1, which suggested that it may be part of the plant assembly chaperone PBAC1/2 complex (Figure 5C).

Because these interactions were analyzed in yeast, which contain their own assembly chaperones that might interfere with interactions between plant subunits, we wanted to verify that PAP1 interacted with PBAC1 \textit{in planta}. To do this we tested several pairwise interactions by bimolecular fluorescent complementation (BiFC) via transient expression in \textit{Nicotiana benthamiana} leaves. Figure 5D shows confocal images of transiently expressed PAP1, PBAC1, PBAC2, and PBAC3 with either the N- or C-terminal half of YFP (NYFP and CYFP respectively) attached as a translational fusion to the N-terminus of each putative assembly chaperone. As controls, PAP1 and PBAC1-3 were tested for auto-activation against NYFP or CYFP alone with no strong auto-activation being observed (Figure S10B). We again observed interactions between PBAC1 and PBAC2, regardless of their attachment to the N or C terminal halves of YFP based on their strong fluorescent intensity (Figure 5D). Additionally, we saw an interaction between PAP1 and PBAC1, showing that PAP1 can interact with PBAC1 \textit{in planta}.  Consistent with our Y2H data, there was no evidence of strong interaction between PAP1 and PBAC3 (Figure 5D).

\subsection{Inhibition of the Proteasome Results in Formation of Distinct Proteasome Sub-Species Containing Putative CP Assembly Chaperones}
Upon inhibition with the proteasomal inhibitor MG132, most proteasome genes are coordinately upregulated by a pair of NAC transcription factors, NAC53 and NAC78, as the plants attempt to synthesize more proteasomes in an effort to increase degradation capacity \citep{gladman16}. Additionally, after prolonged inhibition the complex becomes heavily ubiquitylated and is turned over via autophagy, likely as a clearing mechanism for inhibited complexes \citep{marshall15}. We reasoned that treatment with MG132 might lead to an increase in the population of newly assembling proteasomes, potentially allowing us to observe proteasome assembly intermediates. As such, proteasomes were purified in the presence of ATP from \textit{PAG1::PAG1-FLAG pag1-1} tissue treated for 16 hours with or without MG132. A silver stain of SDS-PAGE-separated proteins affinity-purified from MG132-treated tissue showed successful purification of the 26S proteasome under these conditions (Figure 6A) with the only notable difference in the treated sample being an increased association of PA200, which was also observed by Book et al. \citep{book10}. An anti-ubiquitin immunoblot of the same samples (Figure 6B), showed extensive ubiquitylation of the particle consistent with data observed by Marshall et al \citep{marshall15}.

Non-denaturing native-PAGE of affinity-purified proteasomes were performed to determine if any novel complexes could be observed. Intriguingly, silver staining of samples affinity-purified from MG132-treated tissue revealed a smear below the canonical CP band (Figure 6B). Additionally, extra bands were observed above the canonical CP band, which may represent stalled intermediates with the alternate capping particle PA200 \citep{li07}. To identify the proteins contained in the bands shown in Figure 7B, we cut the corresponding gel slices, trypsin-digested the proteins, and then analyzed the resulting peptides via MS/MS. A LFQ-MS approach was used to quantify the proteins present in each sample \citep{gemperline16}. Proteins identified in gel slices obtained from both MG132-treated and untreated control samples were clustered based on relative abundance using hierarchical clustering. The clusters were then visualized via a heat map showing that the RP and CP proteins cluster away from one another in these samples (Figure 6C), consistent with their separation by native-PAGE. Furthermore, an outgroup that includes the putative assembly chaperones PBAC1-4, Ump1, and PAP1, plus the accessory factors PA200, PTRE1, as well as ubiquitin, is found in the CP cluster (Figure 6C).

The proteins identified in gel slices below the canonical CP band in both MG132-treated and untreated control samples (Figure 7B) contained a large abundance of CP $\alpha$-subunits, with very few $\beta$-subunits (Figure 6C). In addition to this set of $\alpha$-subunits, the previously mentioned CP-specific putative assembly chaperones PBAC1-4 were also observed, as was the plant-specific PAP1 protein and UMP1b. PBAC3 and PBAC4 were only identified in the slice below the canonical CP band. Slices 1-5 contained mostly CP subunits with very few, if any, RP subunits (Figure 6C). Slice 2, above the canonical CP band, from both treated and untreated samples also contained PBAC1, PBAC2, and PAP1, suggesting that this band may represent an assembly intermediate of the plant CP. All CP subunits and the alternate capping particle PA200 were identified in slice 3, suggesting that this band represents CP capped with PA200. Slices 4 and 5 were observed only in proteasomes purified from MG132 treated tissue (Figure 6B, and Table S8), and interestingly, slice 4 contained both the PA200 alternate capping particle, and the assembly chaperones PBAC1, PBAC2, and PAP1 along with most of the CP subunits, suggesting that this may be a PA200 containing assembly intermediate. Slice 5 likely represented a doubly capped PA200-CP-PA200 species, as no other putative assembly chaperones were present, and a strong signal for PA200, and the various CP subunits was observed.

>>>>

\subsection{Statistical Analyses of LFQ-MS/MS Data Show Affinity Preparations Targeting Either the CP or RP Specifically Enrich for Their Respective Subcomplexes}
The LFQ-MS/MS data allowed us to perform a more formal statistical test for the enrichment of the RP over the CP in samples affinity purified from the RP subunits FLAG-RPT4a/b, and for the enrichment of the CP over the RP in samples affinity purified from CP subunit PAG1-FLAG. We estimated the distribution of RP and CP subunits in these samples using kernel density estimations (KDE) of MaxLFQ values as compared to our wild-type mock-affinity purifications as a negative control (Figure \ref{fig:volcanos1} below each volcano plot, and larger plots in Figure \ref{fig:supkde}).  As the KDE distributions were not normal, two non-parametric statistical tests, Kolmogorov-Smirnov (KS) and median test, were used to determine if there was specific enrichment of particular proteasome sub-complexes (RP vs CP) from the different affinity purifications. The KS test determines if the two distributions are different in shape or position, and the median test determines if the distribution’s medians are statistically different.

\begin{sidewaysfigure}[p]
	\centering
	\includegraphics[width=\columnwidth]{Proteasome/Volcanosplit1.png}
	\mycaption{Volcano Plots comparing proteasome affinity purifications under both plus and minus ATP conditions relative to WT controls, allow identification of statistically significant interacting partners for the proteasome}
	{Volcano plots comparing affinity purifications for PAG1-FLAG \textbf{(A and B)}, FLAG-RPT4a \textbf{(C and D)}, and FLAG-RPT4b \textbf{(E and F)} against their respective WT mock affinity purification control are shown. The top panels \textbf{(A, C, and E)} show comparisons for samples purified in the absence of ATP, while the lower panels \textbf{(B, D, and F)} show comparisons for samples purified in the presence of ATP. Two-dimensional Kernel Density Estimations (KDE) are shown for CP subunits in red and RP subunits in blue. Larger KDE plots are available in Figure \ref{fig:supkde}. CP subunits are labeled as red squares, while RP subunits are labeled as blue squares. Proteins outside the dashed lines are statistically significantly differentially represented in purified samples relative to control as judged by a significant analysis of microarray or (SAM) test at 0.01 false discovery rate. Proteins likely involved in CP assembly are shown as green squares, while proteins likely involved in RP assembly are shown as yellow squares. Known proteasome associated proteins or PAPs are labeled as black squares, while unknown PAPs are labeled in grey squares. Proteins identified that did not reach SAM significance are labeled as grey circles.}
	\label{fig:volcanos1}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
	\ContinuedFloat
	\centering
	\includegraphics[width=\columnwidth]{Proteasome/Volcanosplit2.png}
	\mycaption{Volcano Plots comparing proteasome affinity purifications under both plus and minus ATP conditions relative to WT controls, allow identification of statistically significant interacting partners for the proteasome}
	{Volcano plots comparing affinity purifications for PAG1-FLAG \textbf{(A and B)}, FLAG-RPT4a \textbf{(C and D)}, and FLAG-RPT4b \textbf{(E and F)} against their respective WT mock affinity purification control are shown. The top panels \textbf{(A, C, and E)} show comparisons for samples purified in the absence of ATP, while the lower panels \textbf{(B, D, and F)} show comparisons for samples purified in the presence of ATP. Two-dimensional Kernel Density Estimations (KDE) are shown for CP subunits in red and RP subunits in blue. Larger KDE plots are available in Figure \ref{fig:supkde}. CP subunits are labeled as red squares, while RP subunits are labeled as blue squares. Proteins outside the dashed lines are statistically significantly differentially represented in purified samples relative to control as judged by a significant analysis of microarray or (SAM) test at 0.01 false discovery rate. Proteins likely involved in CP assembly are shown as green squares, while proteins likely involved in RP assembly are shown as yellow squares. Known proteasome associated proteins or PAPs are labeled as black squares, while unknown PAPs are labeled in grey squares. Proteins identified that did not reach SAM significance are labeled as grey circles.}
	\label{fig:volcanos2}
\end{sidewaysfigure}

The KDE distribution for the CP as compared to the RP from samples affinity purified in the absence of ATP using PAG1-FLAG showed both the KS and the median \textit{p}-values being much less than 0.01, at 1.74E-10 and 4.3E-10, respectively (Figure \ref{fig:volcanos1} and \ref{fig:supkde} A). This suggests that the distributions are different, and that their medians were different with a greater than 20 fold increase in CP over RP. Conversely the KDE distributions for the samples affinity purified in the presence of ATP using PAG1-FLAG (Figure \ref{fig:volcanos2} and \ref{fig:supkde} B) overlap to a higher degree, with both the KS and Median \textit{p}-values > 0.01 at 0.401 and 0.256, respectively. This indicates that in samples affinity purified in the presence of ATP that the RP and CP distributions were not significantly different, and that their means were similar. Although not statistically significant, a 1.5 median fold change was observed for the CP over the RP in samples affinity purified in the presence of ATP using PAG1-FLAG suggesting that there may be some CP enriched as compared to the RP. These statistical analyses showed that, as expected, we were able to successfully enrich for the CP over the RP when affinity purifying from PAG1-FLAG expressing tissue.

	Conversely, in samples using the RP-based FLAG-RPT4a/b purified in the absence of ATP, the KDE distributions showed enrichment for the RP over the CP, with a fold change of 3.43 and 3.41 for the RPT4a and RPT4b subunits respectively (Figures \ref{fig:volcanos1} and Figures \ref{fig:supkde} C and E, respectively). Both the KS (3.303E-5 for RPT4a and 5.55E-5 for RPT4b) and median \textit{p}-values (7.11E5 for RPT4a and 7.11E-5 for RPT4b) were < 0.01, suggesting that the two distributions were statistically different and had different medians. Again, contrasting this with the samples purified in the presence of ATP using FLAG-RPT4a and FLAG-RPT4b (Figures \ref{fig:volcanos2} and Figures \ref{fig:supkde} D and F, respectively), the KDE distributions overlap with both the KS (0.017 for RPT4a and 0.058 for RPT4b) and median \textit{p}-values (0.089 for RPT4a and 0.023 for RPT4b) were > 0.01, suggesting that the RP and CP distributions are similar. Although not statistically significant, we still observed a two-fold-change enrichment in both FLAG-RPT4a/b samples purified in the presence of ATP for the RP over the CP. In summary, these KDE distributions and statistical analyses provide further support for enrichment of either the CP or the RP, as expected, when samples were affinity purified in the absence of ATP via PAG1-FLAG, or FLAG-RPT4a/b, respectively.

\subsection{Statistical Analysis of Affinity Purifications Enriched for the RP or CP Identifies Proteasome-Associated Proteins and Putative Assembly Chaperones Specific to Each Subcomplex}
	The ability to affinity-enrich both the CP and the RP from \textit{Arabidopsis} under gentle non-denaturing conditions without the need for high salt washes may enable identification of associated proteins, particularly those which may be more loosely bound. Additionally, targeting the RP or CP enables the identification of proteins that may be associating with either or both subcomplexes specifically. The previous data represented in Figure \ref{fig:MSAssociated} showed the raw MaxLFQ values for some of the relevant associated proteins; however, a formal statistical test against mock affinity purifications was important given the high number of proteins identified and quantified via LFQ-MS/MS. To better understand the suite of proteins that are statistically enriched in samples that target the CP or RP specifically we compared the LFQ-MS/MS data obtained from our affinity purifications against their respective wild-type controls using volcano plots and SAM tests at 0.01 FDR.

Affinity purifications enriching for the CP via PAG1-FLAG, performed either in the presence or absence of ATP (Figure \ref{fig:volcanos1} A and  \ref{fig:volcanos2} B respectively) show statistical enrichment for two orthologs of the UMP1 CP assembly chaperone, UMP1a and UMP1b. The \textit{Arabidopsis} genome encodes a third \textit{UMP1} ortholog, \textit{UMP1c}; however, we have no experimental evidence that UMP1c associates with the proteasome, even though it has several tryptic peptides from an extended C-terminal domain that could differentiate it from UMP1a/b (Figure S4). UMP1a, and UMP1b are considerably higher expressed at 90 and 55 ESTs as compared to UMP1c which had only 7 ESTs \citep{berardini15}, suggesting that UMP1c may be lowly expressed, or possibly a pseudogene.

Intriguingly, these samples also show statistical enrichment for a suite of putative CP assembly chaperones (Proteasome Biogenesis Associated Chaperone) PBAC1-4 (Figure \ref{fig:volcanos1} A and \ref{fig:volcanos2} B). Although their annotation in The \textit{Arabidopsis} Information Resource v10 (TAIR10) was incomplete, an InterProScan of their respective sequences supported these identifications (Table S3A). While PBAC1 was annotated as having a PBAC2 domain, the expectation value of 3.4E-6 was much lower than the expectation value of 1E-29 for the PBAC2 domains in the potential PBAC2 homologue. Additionally, PBAC1 and PBAC2 were previously identified by iterative PSI-BLAST with the human PAC1 and PAC2 orthologs in two separate studies \citep{kusmierczyk11, le07} which aids in our assignment of PBAC1 and PBAC2. This PSI-BLAST based analysis was repeated using human PAC1-4, which identified PBAC1-4 as the top hits for these proteins in \textit{Arabidopsis} (Table S3B). Protein sequence alignments for PBAC1-4 show that these proteins are conserved across plants but that they show little conservation with orthologs outside the plant kingdom with < 15\% protein sequence identity (Figure S5-S8).  All statistically significant interactors from PAG1-FLAG affinity purifications performed in both the presence or absence of ATP are available in Table S4.

As shown in Figure \ref{fig:volcanos1} C-F, UMP1a/b and PBAC1-4 were not significantly enriched in our affinity purifications targeting the RP, suggesting that these proteins interact with the CP specifically. However, affinity purifications that targeted the RP through either FLAG-RPT4a or FLAG-RPT4b showed statistically significant enrichment over controls for the putative orthologs of RP assembly chaperones HSM3, NAS2, and NAS6 (Figure \ref{fig:volcanos1} C-F). Importantly, these putative RP assembly chaperones were also absent from our affinity purifications that targeted the CP, suggesting that these proteins are RP specific interactors. All statistically significant interactors from FLAG-RPT4a and FLAG-RPT4b affinity purified in the presence or absence of ATP are available in Table S5 and Table S6. Several accessory proteins are common to both CP and RP purifications including the alternate capping particle PA200 \citep{book10}, ECM29 that is involved in stabilizing the CP-RP association \citep{lehmann10}, and the recently identified proteasome inhibitor 31 related protein PTRE1, which is involved in modulating proteasome activity in response to auxin \citep{yang16}.

\subsection{A Novel Plant Proteasome-Associated Protein, PAP1, Interacts with a Putative CP Assembly Chaperone}
An intriguing plant-specific protein, named here Proteasome Associated Protein 1 or PAP1 was identified and significantly enriched in affinity preparations that targeted the CP (Figure 4). While PAP1 had no domains of known function, as determined by InterProScan (Table S3A), it did contain a C-terminal HbYX (hydrophobic amino acid, followed by a tyrosine, followed by any amino acid) motif. This HbYX motif is commonly found in proteins that intercalate between the $\alpha$-rings of the CP \citep{kusmierczyk11}. This motif is found in both the plant specific PAP1, and in the assembly chaperone PBAC1 (Figure \ref{fig:papschar} A) as well as the conserved yeast assembly chaperones Pba1 and Pba2 \citep{kusmierczyk11}. However, Pba2/PBAC2 orthologs outside of yeast typically contain a C-terminal HbF motif, with the only notable exception being the moss \textit{Physcomitrella patens} which instead contains a HbYX motif.   To confirm whether PAP1 did indeed interact with the proteasome, we generated transgenic plants expressing HA-tagged PAP1 in the \textit{PAG1::PAG1-FLAG pag1-1} background. Figure \ref{fig:papschar} B shows immunoblots of SDS-PAGE separated samples from an affinity purification of HA-PAP1 utilizing anti-HA beads. HA-PAP1 expressed at very low levels in transgenic plants (Figure \ref{fig:papschar} B, input). However, upon immunopurification and detection with anti-HA antibodies we were able to detect HA-PAP1, the FLAG-tagged CP $\alpha$-subunit PAG1, and the FLAG-less PAG1 product that likely resulted from cleavage of the FLAG tag during overnight incubation \citep{book10}. Low levels of both the CP $\beta$-subunit PBA1, and RPN1 subunit were also detected in these samples.

\begin{FPfigure}[Figure \ref{fig:papschar} \textit{caption follows on next page}]
	\centering
	\includegraphics[width=\columnwidth]{Proteasome/papschar.png}
	\mycaption{PAP1 interacts with the proteasome and with putative assembly chaperone PBAC1}
	{\textbf{(A)} C-terminal sections of protein sequence alignments for PAP1, PBAC1 and PBAC2, show conserved HbYX / HbY/F motifs underlined in red (full alignments in Figures S9, S5, and S6) \textbf{(B)} An anti-HA immunopurification of HA-PAP1 expressed in the PAG1-FLAG background shows affinity enrichment for both PAP1 and the FLAG-tagged PAG1 $\alpha$-subunit of the CP. A very low level of PBA1 is also observed in the elution. \textbf{(C)} A yeast-two-hybrid analysis of putative plant assembly chaperones shows interaction between PBAC1 and PBAC2 independently of whether PBAC1 is used as bait or prey. Similarly, interaction is also detected between PBAC3 and PBAC4 independently of which protein is used as bait. Interaction between PAP1 PBAC1 is also observed. \textbf{(D)} Bi-molecular Fluorescent Complementation (BiFC) with indicated combinations of PAP1, PBAC1, and PBAC2 fused at their N-terminus with either N or C –terminal halves of YFP (N-YFP, C-YFP). BiFC results confirm the results obtained via Y2H in (B) and show that these interactions also occur \textit{in planta} between PBAC1 and PBAC2, and between PBAC1 and PAP1 in either orientation. A control is shown in this figure documenting a lack of auto activation for N-YFP and C-YFP. Additional controls combining N-YFP and C-YFP with their respective N and C terminal PBAC1, PBAC2, PBAC3, and PAP1 controls are shown in Figure S8 along with the full panel from (D) for comparison.}
	\label{fig:papschar}
\end{FPfigure}

To identify which putative \textit{Arabidopsis} assembly chaperones might interact, we performed a yeast two-hybrid (Y2H) interaction assay for all pairwise combinations of PBAC1-4, and PAP1 (Figure \ref{fig:papschar} C). We hypothesized that PAP1 may be a CP assembly chaperone and that it may interact with one or more of the other putative assembly chaperones. The Y2H showed pairwise interaction for PBAC1 and PBAC2, and pairwise interaction for PBAC3 and PBAC4 regardless of whether they were attached to the GAL4 activating or binding domains (Figure \ref{fig:papschar} C). These interactions were consistent with how the CP assembly orthologs in other organisms interact \citep{murata09}.  Taken together these data suggested these proteins might form heterodimeric pairs, like other CP assembly chaperone orthologs. Importantly, we saw no interaction from PBAC1 or PBAC2 to PBAC3 or PBAC4 pairs in this Y2H, suggesting these putative assembly chaperones form separate complexes like their orthologs in mammals and yeast. Interestingly, we observed PAP1 interacting with PBAC1, which suggested that it may be part of the plant assembly chaperone PBAC1/2 complex (Figure \ref{fig:papschar} C).

Because these interactions were analyzed in yeast, which contain their own assembly chaperones that might interfere with interactions between plant subunits, we wanted to verify that PAP1 interacted with PBAC1 \textit{in planta}. To do this we tested several pairwise interactions by bimolecular fluorescent complementation (BiFC) via transient expression in \textit{Nicotiana benthamiana} leaves. Figure \ref {fig:papschar} D shows confocal images of transiently expressed PAP1, PBAC1, PBAC2, and PBAC3 with either the N- or C-terminal half of YFP (NYFP and CYFP respectively) attached as a translational fusion to the N-terminus of each putative assembly chaperone. As controls, PAP1 and PBAC1-3 were tested for auto-activation against NYFP or CYFP alone with no strong auto-activation being observed (Figure S10B). We again observed interactions between PBAC1 and PBAC2, regardless of their attachment to the N or C terminal halves of YFP based on their strong fluorescent intensity (Figure \ref{fig:papschar} D). Additionally, we saw an interaction between PAP1 and PBAC1, showing that PAP1 can interact with PBAC1 \textit{in planta}.  Consistent with our Y2H data, there was no evidence of strong interaction between PAP1 and PBAC3 (Figure ref{fig:papschar} D).

\FloatBarrier

\subsection{Inhibition of the Proteasome Results in Formation of Distinct Proteasome Sub-Species Containing Putative CP Assembly Chaperones}
Upon inhibition with the proteasomal inhibitor MG132, most proteasome genes are coordinately upregulated by a pair of NAC transcription factors, NAC53 and NAC78, as the plants attempt to synthesize more proteasomes in an effort to increase degradation capacity \citep{gladman16}. Additionally, after prolonged inhibition the complex becomes heavily ubiquitylated and is turned over via autophagy, likely as a clearing mechanism for inhibited complexes \citep{marshall15}. We reasoned that treatment with MG132 might lead to an increase in the population of newly assembling proteasomes, potentially allowing us to observe proteasome assembly intermediates. As such, proteasomes were purified in the presence of ATP from \textit{PAG1::PAG1-FLAG pag1-1} tissue treated for 16 hours with or without MG132. A silver stain of SDS-PAGE-separated proteins affinity-purified from MG132-treated tissue showed successful purification of the 26S proteasome under these conditions (Figure \ref{fig:mg132split1} A) with the only notable difference in the treated sample being an increased association of PA200, which was also observed by Book et al. \citep{book10}. An anti-ubiquitin immunoblot of the same samples (Figure \ref{fig:mg132split1} B), showed extensive ubiquitylation of the particle consistent with data observed by Marshall et al \citep{marshall15}.
